---
title: Short Paper
author:
  - name: Alice Anonymous
    url: https://Where/To/Find/You
    email: alice@example.com
    affiliation: Some Institute
    affiliation_url: https://Institute/Website
    orcid_id: 0000-0000-0000-0000
    footnote: 1
address:
  - code: Some Institute
    address: Department, Street, City, State, Zip
footnote:
  - code: 1
    text: "Corresponding Author"
description: |
  This is the description.
  It consists of two paragraphs.
abstract: |
  This is the abstract.
  It consists of two paragraphs.
keywords:
  - One;
  - Two;
  - Three;
  - Four;
  - Five
date: "`r Sys.Date()`"
journal: "An awesome journal"
volume: 10
issue: 4
doi: "10.23915/distill.00010"
slug: anonymous2018
citation_url: https://Your/URL
bibliography: references.bib
csl: elsevier-with-titles.csl
download: true
linenumbers: true
numbersections: true
colorlinks: true
link-citations: true
biblio-style: unsrtnat
header-includes:
  - \biboptions{sort&compress}
  - \hypersetup{bookmarksnumbered=true}
output:
  # PDF output
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
    keep_tex: true
    citation_package: natbib
  # Distill output
  distill::distill_article:
    toc: true
    toc_float: true
    self_contained: false
editor_options:
  markdown:
    wrap: 80
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    echo = FALSE,
    comment = "#>",
    out.width = "100%",
    fig.align = "center",
    fig.path = "figures",
    fig.pos = "!htb"
)
# add a 'biblio-style' option
# otherwise 'plainnat' will always be used
# see https://github.com/rstudio/rticles/issues/395
if (knitr::is_latex_output()) {
    bibstyle <- rmarkdown::metadata[["biblio-style"]]
    if (!(is.null(bibstyle) || length(bibstyle) != 1L || anyNA(bibstyle))) {
        bibstyle <- as.character(bibstyle)
        options("bookdown.post.latex" = function(x) {
          re <- "^\\\\bibliographystyle\\{plainnat\\}$"
          sub(re, sprintf("\\\\bibliographystyle{%s}", bibstyle), x)
        })
    }
}
options(knitr.table.format = function() {
    if (knitr::is_latex_output()) "latex" else "pandoc"
})
library(ggplot2)
```

```{r eval = isTRUE(rmarkdown::metadata$download) && knitr::is_html_output()}
knitr::asis_output('<a href="paper.pdf"><b>[&#x21b7; Download PDF]</b></a>')
```

# Highlights {.unnumbered}

-   First
-   Second
-   Third

# Introduction

@jia2021eplusr proposed an R package for conducting data-driven analytics with
EnergyPlus [@crawley2001energyplus].

The objectives of this paper are to:

1. One
2. Two

# Methodology

## Overview

## Math

Eq. \@ref(eq:equation) gives the definition.

\begin{equation}
  \bar{X}=\frac{1}{n}\sum_{i=1}^nX_i
  (\#eq:equation)
\end{equation}

# Results

Fig. \@ref(fig:plot) gives a pie plot.

```{r plot, fig.cap = "A pie plot"}
targets::tar_read(p_end_use)
```

Table \@ref(tab:table) gives a result table.

```{r table}
targets::tar_read(tbl_end_use) %>% 
  select(category, electricity_per_area) %>%
knitr::kable(
  caption = "A result table",
  col.names = c("Category", "Electricity (kWh/m2)"),
  digits = 2,
  booktabs = TRUE, linesep = "", position = "htbp")
```

# Discussion

# Conclusion

# Data availability {.unnumbered}

The research compendium for this article can be found at
<https://github.com/YouName/RepoName>, hosted at GitHub.

# CRediT authorship contribution statement {.unnumbered}

# Acknowledgements {.unnumbered}

This research was supported by ...

```{r, include = knitr::is_latex_output()}
knitr::asis_output('# References {#references .unnumbered}')
```